Analyzing Information Transfer from Heterogeneous Sources via Precise High-dimensional Asymptotics

### 2021-07-25 revision_journal/multitask.tex
move figs around
start sec 1.2
finish sec 1.2, begin sec 1.3
finish intro

\section{Extension to multiple data sources}\label{sec_same}

@@

\paragraph{Data model.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$. The label vector of the $i$-th task follows a linear model
\begin{align}\label{eq_mtl_data}
    Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}, \text{ for } i=1, 2,\cdots, t.
\end{align}
Similar to Section \ref{sec_main}, we use the first $(t-1)$ datasets as sources to predict the $t$-th task.
However, there is a \text{model shift} between the data sources and the task we would like to predict.
We make several standard assumptions on $X$ and each of $\varepsilon^{(i)}$.
First, $X = Z\Sigma^{1/2}$ is a random matrix satisfying Assumption \ref{assm_big1} (same as $X^{(2)}$).
In particular, the sample size $n$ is greater than the dimension $p$.
Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments up to any order (cf. equation \eqref{eq_highmoments}).
Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from any other $\beta^{(j)}$ for $j \neq i$, the matrix $X$, and $\varepsilon^{(j)}$ for any $j=1,\dots,t$.

@@

@@

\begin{figure}[!t]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/multitask_width.eps}
		\caption{Varying width}
		\label{fig_sec4_width}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/multitask_transfer.eps}
		\caption{Varying sample size and model shift parameter}
		\label{fig_sec4_transfer}
	\end{subfigure}
	\caption{We illustrate the performance of HPS in the random-effect model with $p = 100, t = 10, \sigma = 1/2$.
	Figure \ref{fig_sec4_width} shows that from $1$ to $t = 10$, setting width $r = 1$ gives the lowest excess risk for task $t$.
	The result is averaged over three random seeds.
	This simulation uses $\mu = 0.05$.
	Figure \ref{fig_sec4_transfer} fixes $r = 1$ while varying $\mu$ and $n$. We observe that depending on $\mu$ and $n$, HPS may provide a positive transfer or a negative transfer to task $t$ (similar to Figure \ref{fig_sec3_model_shift}). The precise condition for deciding which one is provided in Claim \ref{claim_re_multi}.}
	\label{fig_sec4}
\end{figure}

Figure \ref{fig_sec4} validates Claim \ref{claim_re_multi}.
First, we see that the empirical excess risk (measured on a particular task) is indeed smallest when the width $r$ is equal to $1$.
Second, we see that HPS provides a positive transfer (to a particular task) depending on the sample size $n$ and the model shift parameter $\mu$.
The results match with the condition (on $\mu$) suggested by our estimates.

>>>>

\section{Extension to multiple sources}\label{sec_same}

@@

\paragraph{Data model.} Suppose we have $t$ datasets whose sample sizes are all equal to $n$ and whose feature covariates are all equal to $X \in \real^{n \times p}$. The label vector of the $i$-th task follows a linear model
\begin{align}\label{eq_mtl_data}
    Y^{(i)} = X \beta^{(i)} + \varepsilon^{(i)}, \text{ for } i=1, 2,\cdots, t.
\end{align}
Similar to Section \ref{sec_main}, we use the first $(t-1)$ datasets as sources to predict the $t$-th task.
However, there is a \text{model shift} between the data sources and the task we would like to predict.
We make several standard assumptions on $X$ and each of $\varepsilon^{(i)}$.
First, $X = Z\Sigma^{1/2}$ is a random matrix satisfying Assumption \ref{assm_big1} (same as $X^{(2)}$).
In particular, the sample size $n$ is greater than the dimension $p$.
Second, every $\varepsilon^{(i)} \in \real^{n}$ is a random vector with i.i.d entries of mean zero, variance $\sigma^2$, and bounded moments up to any order (cf. equation \eqref{eq_highmoments}).
Finally, $\beta^{(i)} \in \real^{p}$ is a fixed vector independent from any other $\beta^{(j)}$ for $j \neq i$, the matrix $X$, and $\varepsilon^{(j)}$ for any $j=1,\dots,t$.
As a remark, the above data model is similar in spirit to the setting of \citet{lounici2011oracle}.
While that work assumes all of the model vectors $\beta^{(1)}, \beta^{(2)}, \dots, \beta^{(t)}$ share the same subset of non-zero coordinates, our result below will apply even when these vectors do not satisfy such conditions.

@@

\begin{figure}[!t]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/multitask_width.eps}
		\caption{Varying width}
		\label{fig_sec4_width}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.8\textwidth]{figures/multitask_b.eps}
		\caption{Varying sample size and model shift parameter}
		\label{fig_sec4_transfer}
	\end{subfigure}
	\caption{We illustrate the performance of HPS in the random-effect model with $p = 100, t = 10, \sigma = 1/2$.
	Figure \ref{fig_sec4_width} shows that from $1$ to $t = 10$, setting width $r = 1$ gives the lowest excess risk for task $t$.
	The result is averaged over three random seeds.
	This simulation uses $\mu = 0.05$.
	Figure \ref{fig_sec4_transfer} fixes $r = 1$ while varying $\mu$ and $n$. We observe that depending on $\mu$ and $n$, HPS may provide a positive transfer or a negative transfer to task $t$ (similar to Figure \ref{fig_sec3_model_shift}). The precise condition for determining the transfer effect can be found in Claim \ref{claim_re_multi}.}
	\label{fig_sec4}
\end{figure}

@@

Figure \ref{fig_sec4} validates the result of Claim \ref{claim_re_multi} in finite dimensions.
First, we see that the empirical excess risk (measured on a particular task) is indeed smallest when the width $r$ is equal to $1$.
Second, we see that HPS provides a positive transfer (to a particular task) depending on the sample size $n$ and the model shift parameter $\mu$.
The results under different $\mu$ values match with the condition in Claim \ref{claim_re_multi}.
